A Comparison of Use-Case Based and Checklist- Based Reading: A Controlled Experiment

### 2015-03-19 rmtw/a6/latex8.tex
sad

\section{Introduction}
%API Design (and a little bit of ecosystems, and a bit of problem statement)
As the software industry and the open source movement steadily grow, the number of public APIs is increasing. APIs can improve the development speed \cite{stylos2006comparing}, contribute to higher quality software \cite{stylos2006comparing} and increase the reusability of software \cite{afonso2012evaluating}.  There is a consensus in that modifying APIs generally should be avoided if possible \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api} \cite{robbes2012developers} since it will require the users of the API to update the code that is accessing the API, thus causing a disruption in the software ecosystem \cite{messerschmitt2005software} that the API's platform is a part of. Most commonly, already deployed APIs are modified due to code refactoring being made \cite{dig2005role} \cite{xing2006refactoring}. 
%Software Evolution 
In the discipline of Software Evolution, such updates to software are studied from an evolutionary standpoint. Software can be updated for different reasons and these motives can be grouped into corrective, adaptive, perfective and preventive changes \cite{lientz1980software} \cite{iso}.

>>>>

\section{Introduction}
%API Design (and a little bit of ecosystems, and a bit of problem statement)
As the software industry and the open source movement steadily grow, the number of public APIs is increasing. APIs can improve the development speed \cite{stylos2006comparing}, contribute to higher quality software \cite{stylos2006comparing} and increase the reusability of software \cite{afonso2012evaluating}.  There is a consensus in that modifying APIs generally should be avoided if possible \cite{google_talk} \cite{mcdonnell2013empirical} \cite{robbes2012developers} \cite{henning2007api} \cite{robbes2012developers} since it will require the users of the API to update the code that is accessing the API, thus causing a disruption in the software ecosystem that the API's platform is a part of \cite{messerschmitt2005software}. Most commonly, already deployed APIs are modified due to code refactoring being made \cite{dig2005role} \cite{xing2006refactoring}. 
%Software Evolution 
In the discipline of Software Evolution, such updates to software are studied from an evolutionary standpoint. Software can be updated for different reasons and these motives can be grouped into corrective, adaptive, perfective and preventive changes \cite{lientz1980software} \cite{iso}.
